---
title: "00_NHANES_LODs"
output: html_document
date: '2024-08-15'
---

# Calculation of detection frequencies 
Detection frequencies of each chemical.  
Using detection comments if directly available, or comments from a compiled dataset from kaggle if not: 
https://www.kaggle.com/datasets/nguyenvy/nhanes-19882018?resource=download
```{r}
library(tidyverse)
library(haven)
load("NHANES_Exposures_Clean.RData")

clock_dat <- read_sas("dnmepi.sas7bdat")
clock_dat <- clock_dat %>% filter(SEQN %in% df$SEQN)
```

Phthalates
```{r}
varlist <- c("URXMBP","URXMCP","URXMEP","URXMHP","URXMNP","URXMOP","URXMZP","URXDAZ",
             "URXDMA", "URXEQU","URXETD","URXETL","URXGNS","URXP09")
commentlist <- paste0("URD", substr(varlist, 4, 6), "LC") # conversion between variable and comment code

check <- read.csv("comments_clean.csv") 
check <- check %>% filter(SEQN %in% clock_dat$SEQN)
check <- check %>% 
  select(SEQN, all_of(commentlist))

sum_df <- cbind(varlist, commentlist, rep(77777, length(varlist)), rep(77777, length(varlist)))
colnames(sum_df) <- c("Exposure", "Comment", "Detect", "Nondetect")

for(i in 1:length(commentlist)){
  
  sub <- check[, c("SEQN", commentlist[i])]
  sub <- na.omit(sub)
  
  if(length(table(sub[, 2])) > 2){
    stop("Unexpected Values in Comment Code")
  }
  
  sum_df[i, 3] <- length(which(sub[, 2] == 0))
  sum_df[i, 4] <- length(which(sub[, 2] == 1))
  
}

phthal <- sum_df

```

VOCs
Detection comment codes found in main dataset. 
```{r}
varlist <- c("LBXV4C", "LBXVBF","LBXVBM",
             "LBXVBZ","LBXVCF","LBXVCM","LBXVCT","LBXVDB","LBXVEB","LBXVME","LBXVOX",
             "LBXVST", "LBXVTC","LBXVTO","LBXVXY")
commentlist <- paste0("LBD", substr(varlist, 4, 6), "LC")

sub <- df %>% 
  select(all_of(commentlist))
sum_df <- cbind(varlist, commentlist, rep(77777, length(varlist)), rep(77777, length(varlist)))
colnames(sum_df) <- c("Exposure", "Comment", "Detect", "Nondetect")

for(i in 1:length(commentlist)){
  
  if(length(table(sub[, i])) > 6){
    stop("Unexpected Values in Comment Code") 
  }
  
  # coded multiple versions of same variables
  sum_df[i, 3] <- length(which(sub[, i] == 0)) + length(which(sub[, i] == "detectable result")) + 
    length(which(sub[, i] == 2)) +  
    length(which(sub[, i] == "detectable result and exceeds the calibrated range of assay"))
  sum_df[i, 4] <- length(which(sub[, i] == 1)) + length(which(sub[, i] == "below detectable limit"))
  
}

voc <- sum_df

```

Pesticides
```{r}
varlist <- c("URX24D", "URX25T","URXATZ","URXCBF",
             "URXDEE","URXCPM","URXPAR",
             "URXPPX","URXOP1","URXOP2","URXOP3","URXOP4","URXOP5","URXOP6","URX4FP",
             "URXCB3","URXCCC","URXTCC","URXOPM")
# URDDIZLC (URXDIZ) not present, manually add after
commentlist <- paste0("URD", substr(varlist, 4, 6), "LC")

check <- read.csv("comments_clean.csv") 
check <- check %>% filter(SEQN %in% clock_dat$SEQN)
check <- check %>% 
  select(SEQN, all_of(commentlist))

sum_df <- cbind(varlist, commentlist, rep(77777, length(varlist)), rep(77777, length(varlist)))
colnames(sum_df) <- c("Exposure", "Comment", "Detect", "Nondetect")

for(i in 1:length(commentlist)){
  
  sub <- check[, c("SEQN", commentlist[i])]
  sub <- na.omit(sub)
  
  if(length(table(sub[, 2])) > 2){
    stop("Unexpected Values in Comment Code")
  }
  
  sum_df[i, 3] <- length(which(sub[, 2] == 0))
  sum_df[i, 4] <- length(which(sub[, 2] == 1))
  
}

pest <- sum_df

# add missing pesticide (URDDIZLC (URXDIZ))
pest <- rbind(pest, c("URXDIZ", "URDDIZLC", 
                      table(df$URDDIZLC)[1], table(df$URDDIZLC)[2]))

```

Metals
```{r}
varlist <- c("URXUBA","URXUBE","URXUCO","URXUCS","URXUMO","URXUPB",
             "URXUPT","URXUSB","URXUTL","URXUTU")
commentlist <- paste0("URD", substr(varlist, 4, 6), "LC")

check <- read.csv("comments_clean.csv") 
check <- check %>% filter(SEQN %in% clock_dat$SEQN)
check <- check %>% 
  select(SEQN, all_of(commentlist))

sum_df <- cbind(varlist, commentlist, rep(77777, length(varlist)), rep(77777, length(varlist)))
colnames(sum_df) <- c("Exposure", "Comment", "Detect", "Nondetect")

for(i in 1:length(commentlist)){
  
  sub <- check[, c("SEQN", commentlist[i])]
  sub <- na.omit(sub)
  
  if(length(table(sub[, 2])) > 2){
    stop("Unexpected Values in Comment Code")
  }
  
  sum_df[i, 3] <- length(which(sub[, 2] == 0))
  sum_df[i, 4] <- length(which(sub[, 2] == 1))
  
}

metals <- sum_df
metals <- rbind(metals, 
                c("URDUCD", "URDUCDLC", table(df$URDUCDLC)[1], 
                  table(df$URDUCDLC)[2] + table(df$URDUCDLC)[3]))

```

Dioxins
Detection comment codes found in main dataset. 
```{r}
varlist <- c("LBX052LA","LBX066LA", "LBX074LA",  "LBX099LA", "LBX101LA" ,"LBX105LA" ,
             "LBX118LA", "LBX128LA" ,"LBX138LA", "LBX146LA", "LBX153LA" ,"LBX156LA",
             "LBX157LA", "LBX167LA" ,"LBX170LA", "LBX172LA",  "LBX177LA" , "LBX178LA", 
             "LBX180LA",  "LBX183LA" , "LBX187LA", "LBXD01LA",  "LBXD03LA" ,"LBXD04LA",
             "LBXD05LA",  "LBXD07LA" ,"LBXF01LA",  "LBXF02LA",  "LBXF03LA" ,"LBXF04LA",
             "LBXF05LA","LBXF06LA" ,"LBXF07LA", "LBXF08LA", "LBXF10LA" ,"LBXPCBLA", 
             "LBXTC2LA", "LBXTCDLA" ,"LBXGHCLA", "LBXHCBLA",  "LBXHPELA","LBXHXCLA", 
             "LBXMIRLA", "LBXODTLA","LBXOXYLA", "LBXPDELA", "LBXPDTLA","LBXTNALA")
commentlist <- paste0("LBD", substr(varlist, 4, 6), "LC")
sub <- df %>% 
  select(all_of(commentlist))
sum_df <- cbind(varlist, commentlist, rep(77777, length(varlist)), rep(77777, length(varlist)))
colnames(sum_df) <- c("Exposure", "Comment", "Detect", "Nondetect")

for(i in 1:length(commentlist)){
  
  if(length(table(sub[, i])) > 2){
    stop("Unexpected Values in Comment Code")
  }
  
  sum_df[i, 3] <- length(which(sub[, i] == 0))
  sum_df[i, 4] <- length(which(sub[, i] == 1))
  
}

dioxins <- sum_df

```

Cadmium, Lead, Mercury, Cotinine & Nutritional Biochemistries
```{r}
varlist <- c("LBXBPB","LBXBCD","LBXCOT")
commentlist <- paste0("LBD", substr(varlist, 4, 6), "LC")

check <- read.csv("comments_clean.csv") 
check <- check %>% filter(SEQN %in% clock_dat$SEQN)
check <- check %>% 
  select(SEQN, all_of(commentlist))

sum_df <- cbind(varlist, commentlist, rep(77777, length(varlist)), rep(77777, length(varlist)))
colnames(sum_df) <- c("Exposure", "Comment", "Detect", "Nondetect")

for(i in 1:length(commentlist)){
  
  sub <- check[, c("SEQN", commentlist[i])]
  sub <- na.omit(sub)
  sub <- sub %>% distinct(SEQN, .keep_all = TRUE) 
  
  if(length(table(sub[, 2])) > 2){
    stop("Unexpected Values in Comment Code")
  }
  
  sum_df[i, 3] <- length(which(sub[, 2] == 0))
  sum_df[i, 4] <- length(which(sub[, 2] == 1))
  
}

cad <- sum_df

```

Perfluoroalkyl Chemicals (not used for primary analysis)
```{r}
varlist <- c("SEPAH","SMPAH","SPFDE","SPFDO",
             "SPFHP","SPFHS","SPFNA","SPFOA",
             "SPFOS","SPFSA","SPFUA")
commentlist <- paste0(substr(varlist, 1, 5), "LC")
sub <- df %>% 
  select(all_of(commentlist))
sum_df <- cbind(varlist, commentlist, rep(77777, length(varlist)), rep(77777, length(varlist)))
colnames(sum_df) <- c("Exposure", "Comment", "Detect", "Nondetect")

for(i in 1:length(commentlist)){
  
  if(length(table(sub[, i])) > 2){
    stop("Unexpected Values in Comment Code")
  }
  
  sum_df[i, 3] <- length(which(sub[, i] == 0))
  sum_df[i, 4] <- length(which(sub[, i] == 1))
  
}

pfas <- sum_df

```


# Merge All Data
```{r}
sums <- rbind(phthal, voc, pest, metals, dioxins, cad, pfas)
sums <- as.data.frame(sums)
sums$Detect <- as.numeric(sums$Detect)
sums$Nondetect <- as.numeric(sums$Nondetect)

sums$detect_freq <- sums$Detect / (sums$Detect + sums$Nondetect)
sums$keep <- ifelse(sums$detect_freq >= 0.5, "Keep", "Drop")
sums$pfas_flag <- ifelse(sums$Exposure %in% pfas[, 1], "PFAS", "")

# creatinine-adjustment flags
sums$creatinine <- ifelse(sums$Exposure %in% phthal[, 1], "URXUCR.x", 
                    ifelse(sums$Exposure %in% pest[, 1], "URXUCR.y",
                           ifelse(sums$Exposure %in% metals[, 1], "URXUCR", "")))


write.csv(sums, file = "NHANES_LODs.csv")
```

